Colorado-Pennsylvania Redistricting Comparison

### 2020-12-07 co_pa_comparison.Rmd
remove unused function

# function to plot bias of each simulation instance (fig. 5)
# (code adapted from the paper replication code paper/fig5_fig6/fig5_fig6.R)
plot_sim_bias <- function(xax, storebias, range=0.1) {
    bias_min <- - (range - -1 * range) * 1 / 2
    bias_max <- (range - -1 * range) * 1 / 2
    # plot xax
    test <- (1 - -1) * (tapply(storebias,  round(xax, 4), mean) - bias_min) / 
        (bias_max - bias_min) + -1
    x <- as.numeric(names(test)) 
    n <- table(round(xax, 4))
    par(mfrow=c(1,1), mar=c(4.1, 4.3, 2.1, 1.0))
    # colrep <- rep('black', length(test[x<.05]))
    colrep <- rep('black', length(test))
    plot(
        # x[x<.05], test[x<.05], cex=n^(1/100), pch=16,
        x, test, cex=n^(1/100), pch=16,
        ylim=c(0, max(test)),
        main='Partisan Bias of Simulated Plans',
        xlab='% of Precincts Switched From Original District',
        ylab='Partisan Bias towards Democrats',
        xaxt='n',
        cex.lab=1.6,
        cex.axis=1.7,
        cex.main=1.6,
        col=colrep
     )
    # axis(1, seq(0, 0.1, by=0.01), c('0%', '1%', '2%', '3%', '4%', '5%', '6%', '7%', '8%', '9%', '10%'), cex.axis=1.7)
    abline(h=(1 - -1) * (storebias[1] - bias_min) / (bias_max - bias_min) + -1)
    abline(h=0, col='red', lty='dashed')
}

plot_swap_summary <- function(map, algout, storebias, xax, mindev=0.02875, maxdev=0.03125, dist=3) {
    ind <- which(storebias == min(storebias[xax < maxdev & xax > mindev]))[1]
    orig_map <- algout[,1] + 1
    min_map <- algout[,ind] + 1
    unchanged <- orig_map == min_map
    subset <- orig_map == 1 | min_map == 1
    col <- ifelse(orig_map[subset] == min_map[subset], 'white',
                  ifelse(orig_map[subset] == 1, 'blue', 'red'))

    dist_idx <- orig_map == dist | min_map == dist
    dist_col <- ifelse(orig_map[dist_idx] == min_map[dist_idx], 'white',
                       ifelse(orig_map[dist_idx] == dist, 'blue', 'red'))

    par(mfrow=c(2,2), mar=c(5.1, 4.3, 3.1, 0.2))
    # CD 1
    plot(
        density(
            na.omit(
                dem_voteshare[subset & orig_map[subset] == min_map[subset]]
            ), from=0, to=1
        ),
        xlim=c(0, 1),
        xlab='Vote Share for Democratic Congressional Candidate',
        lwd=2,
        main='Distribution of Democratic Voteshare for District 1',
        cex.lab=1.6,
        cex.axis=1.7,
        cex.main=1.6
    )
    lines(
        density(
            na.omit(
                dem_voteshare[subset & orig_map[subset] == 1 & min_map[subset] != 1]
            ), from=0, to=1
        ), col='blue',
        lwd=2,
        lty='dashed'
    )
    lines(
        density(
            na.omit(
                em_voteshare[subset & orig_map[subset] != 1 & min_map[subset] == 1]
            ), from=0, to=1
        ), col='red',
        lwd=2,
        lty='dotdash'
    )
    legend('topleft', col=c('black', 'blue', 'red'),
           lwd=2, legend=c('Not Swapped', 'Swapped Out', 'Swapped In'),
           lty=c(1, 2, 6),
           bty='n', cex=1.6)
    plot(mapsub_1, col=mapsub$col, lwd=1,
         main='Congressional District 1',
        cex.lab=1.6,
        cex.axis=1.7,
        cex.main=1.6)
    legend('topleft', col=c('black', 'blue', 'red'),
           pt.bg=c('white', 'blue', 'red'),
           pch=22,
           legend=c('Not Swapped', 'Swapped Out', 'Swapped In'),
           bty='n', cex=1.6)
    # CD 11
    plot(
        density(
            na.omit(
                mapsub_dist$dem_voteshare[mapsub_dist$orig_map == mapsub_dist$min_map]
            ), from=0, to=1
        ),
        ylim=c(0,6),
        xlim=c(0, 1),
        xlab='Vote Share for Democratic Congressional Candidate',
        lwd=2,
        main='Distribution of Democratic Voteshare for District 3',
        cex.lab=1.6,
        cex.axis=1.6,
        cex.main=1.6
    )
    lines(
        density(
            na.omit(
                mapsub_dist$dem_voteshare[mapsub_dist$orig_map == dist & mapsub_dist$min_map != dist]
            ), from=0, to=1
        ), col='blue',
        lwd=2,
        lty='dashed'
    )
    lines(
        density(
            na.omit(
                mapsub_dist$dem_voteshare[mapsub_dist$orig_map != dist & mapsub_dist$min_map == dist]
            ), from=0, to=1
        ), col='red',
        lwd=2,
        lty='dotdash'
    )
    plot(mapsub_dist, col=mapsub_dist$col, lwd=1,
         main='Congressional District 3',
        cex.lab=1.5,
        cex.axis=1.7,
        cex.main=1.6)
}
```

@@

```{r}
# TODO: are these the correct columns to use from Colorado data?
co_sim_bias <- calc_sim_bias(co_sim, co$GOV18D, co$GOV18R)
plot_sim_bias(xax, co_sim_bias)
```

>>>>

# function to plot bias of each simulation instance (fig. 5)
# (code adapted from the paper replication code paper/fig5_fig6/fig5_fig6.R)
plot_sim_bias <- function(xax, storebias, range=0.1) {
    bias_min <- - (range - -1 * range) * 1 / 2
    bias_max <- (range - -1 * range) * 1 / 2
    # plot xax
    test <- (1 - -1) * (tapply(storebias,  round(xax, 4), mean) - bias_min) / 
        (bias_max - bias_min) + -1
    x <- as.numeric(names(test)) 
    n <- table(round(xax, 4))
    par(mfrow=c(1,1), mar=c(4.1, 4.3, 2.1, 1.0))
    # colrep <- rep('black', length(test[x<.05]))
    colrep <- rep('black', length(test))
    plot(
        # x[x<.05], test[x<.05], cex=n^(1/100), pch=16,
        x, test, cex=n^(1/100), pch=16,
        ylim=c(0, max(test)),
        main='Partisan Bias of Simulated Plans',
        xlab='% of Precincts Switched From Original District',
        ylab='Partisan Bias towards Democrats',
        xaxt='n',
        cex.lab=1.6,
        cex.axis=1.7,
        cex.main=1.6,
        col=colrep
     )
    axis(
      1,
      seq(0, max(x), by=0.05),
      as.character(seq(0, max(x), by=0.05)),
      cex.axis=1.7
    )
    abline(h=(1 - -1) * (storebias[1] - bias_min) / (bias_max - bias_min) + -1)
    abline(h=0, col='red', lty='dashed')
}
```

@@

```{r}
# TODO: are these the correct columns to use from Colorado data?
co_sim_bias <- calc_sim_bias(co_sim, co$GOV18D, co$GOV18R)
plot_sim_bias(xax, co_sim_bias)
```
```{r}
dev.print(png, 'figures/bias.png')
```
